Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-09-11 manuscript.qmd
display of the lambda hyperparameter selected for lasso and removing paletteer dependancy

```{r}
library ("readxl") # version 1.4.3
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("paletteer") # version 1.4.0
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("treeshap") # version 0.3.1
library ("shapviz") # version 0.9.3
library ("kableExtra") # version 1.3.4
```

@@

Dark2 = paletteer_d("RColorBrewer::Dark2")
```

@@

@@

    data_lasso %>% 
            select (- pmid, - e.cum, - e.rel, - dataset, - country) %>% 
            as.matrix
)

@@

    data_scenarios_lasso %>% as.matrix
)

>>>>

```{r}
library ("readxl") # version 1.4.3
library ("ggplot2") # version 3.4.4
library ("gridExtra") # version 2.3
library ("dplyr") # version 1.1.2      
library ("tibble") # version 3.2.1
library ("tidyr") # version 1.3.0
library ("ALFAM2") # version 3.7
library ("randomForest") # version 4.7.1.1
library ("xgboost") # version 1.7.6.1
library ("glmnet") # version 4.1.8
library ("treeshap") # version 0.3.1
library ("shapviz") # version 0.9.3
library ("kableExtra") # version 1.3.4
```

@@

Dark2 = c ("#1B9E77FF", "#D95F02FF", "#7570B3FF", "#E7298AFF", "#66A61EFF", "#E6AB02FF", "#A6761DFF", "#666666FF") 
```

@@

```{r}
# lambda.1se is the largest value of lambda such that error is within 1 standard error of the 
# lambda that minimizes the mean cross_validated error
lasso_model$lambda.1se
```

@@

    data_lasso %>% 
            select (- pmid, - e.cum, - e.rel, - dataset, - country) %>% 
            as.matrix,

    s = "lambda.1se"
)

@@

    data_scenarios_lasso %>% as.matrix,

    s = "lambda.1se"
)
